Optimal (Multiway) Spatial Joins

### 2024-05-19 msj.tex
yufei

From the theory perspective, SJs are best understood when $k = 2$, i.e., the {\em pairwise} scenario, where the problem can be solvable in $O(n \log n + \out)$ time by the standard planesweep technique \cite{bcko08}.

>>>>

From the theory perspective, SJs are best understood when $k = 2$, i.e., the {\em pairwise} scenario, where the problem can be solvable in $O(n \log n + \out)$ time by the standard planesweep technique \cite{bcko08}. However, the problem becomes significantly more challenging as soon as $k$ reaches 3, i.e., the {\em multiway} scenario. All the solutions developed (see \cite{mp01,???} and the references therein) before 2022 all suffer from a worst-case time complexity of $O(n^k)$, namely, no better than the naive method that simply enumerates the entire cartesian product $R_1 \times R_2 \times ... \times R_k$.
